Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-27 Documents/Euler/Benchmarks1D/draft.tex
changes to test 12 and experiments intro

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests \ee{Add more descriptive caption}}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 400 cells. The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
     \includegraphics[width=.475\textwidth]{vel_T12_400.png}	
    \end{tabular}
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
\end{figure}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}
     \includegraphics[width=.475\textwidth]{prs_T12_400.png}
    \end{tabular}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_2000} and Figure~\ref{fig:den_T12_400}, computed with 2000 cells (left) and 400 cells (right).}
\end{figure}

@@

>>>>

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}. The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$. These initial conditions are then advanced to time $T$.}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_2000.png}
     \includegraphics[width=.475\textwidth]{prs_T12_2000.png}	
    \end{tabular}
  \end{center}
 \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_2000}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_2000}~computed with 400 cells. The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{vel_T12_400.png}
     \includegraphics[width=.475\textwidth]{prs_T12_400.png}	
    \end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T12_400}:
  velocity (left panel) and pressure (right panel)}
\end{figure}

@@

\section{Conclusion}
